Synthesizing Quotient Lenses

### 2018-03-09 papers/QuotientLenses/main.tex

We found that 10 of Optician's 39 benchmarks required modifications to be
bijective. We found that 4 of Optician's 39 benchmarks required modifications to
be in bijective correspondence when in canonical form.\saz{Is this somehow where
  the 14 = 10+4 points in Fig. 10 come from?}\saz{Do these 10 and 4 intersect?}
Furthermore, we found that all eight of the data.gov examples required no
modifications to be in bijective correspondence when in canonical
form.\BCP{Is this surprising?  We could have chosen the examples so that
  this is true.} While we
did not put the data.gov examples into a form suitable for pre-QRE
Optician\bcp{What does that mean?}, we
found that only four of the eight data.gov examples did not require
canonization, so making them suitable for pre-QRE Optician would have required 
changes to of four of the data.gov formats.  Here again, we see that QREs add
significant expressive power.

@@

Also notable is one of the data.gov examples, which converts demographic
statistics by zip code from xml form into rdf form. This took longer because it
was an exceptionally large format, converting over 40 fields.\saz{We need to
  explain more detail here.  I guess this is about the last benchmark in Fig. 11
  (b), which takes a long time?\bcp{It's a bit hidden in the figure...}}  We
added in additional fields to make this 
format suitable for Optician, which took over 15 seconds synthesize the modified
lens.\saz{This needs more context, explanation.}

@@

\bibliographystyle{plain}
\bibliography{local}

>>>>

We found that 10 of Optician's 39 benchmarks required modifications to be
bijective. Of these We found that 4 of Optician's 39 benchmarks required
modifications to be in bijective correspondence when in canonical form.
Furthermore, we found that all eight of the data.gov examples required no
modifications to be in bijective correspondence when in canonical
form.\BCP{Is this surprising?  We could have chosen the examples so that
  this is true.} While we
did not put the data.gov examples into a form suitable for pre-QRE
Optician\bcp{What does that mean?}, we
found that only four of the eight data.gov examples did not require
canonization, so making them suitable for pre-QRE Optician would have required
changes to of four of the data.gov formats. Here again, we see that QREs add
significant expressive power.

@@

Also notable is one of the data.gov examples, which converts demographic
statistics by zip code from xml form into rdf form.\bcp{It's a bit hidden in the figure...} To validate this performance
was not due to our overhead, we modified this format to be bijective, so it
could be input into Optician. Optician took over 15 seconds synthesize this
modified lens. We believe this conversion took longer because the input formats
were exceptionally large, requiring conversions between over 40 fields.

@@

\bcp{Some of the citations need some love---e.g., the first one.}
\bibliographystyle{plain}
\bibliography{local}
